### 2023-12-15 main.tex
Appendices B,C,D

To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{a}^{x})=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$. This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation

@@

We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ and we obtain

@@

		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{\alpha}^{x})\dt

@@

	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1}^{N}n_{A}^{x}n_{d}^{x+1}-\sum_{B=1}^{N}n_{d}^{x}n_{B}^{x+1}\\

@@

In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{D}^{x+1}$, when $A=d$ (here we call $D=h_{c}(B)$); a contribution $n_{A}^{x}n_{h_{c}(B^{'})}^{x+1}$, where we denoted by $B^{'}\in \{1,\ldots,N\}$ the type of particle such that $h_{c}(B^{'})=d$. Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that in the above equation $h_{c}(B^{'})\neq d$ and $h_{c}(B^{'})\neq N$. Thus we obtain 

@@

		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{A,B=1}^{N}\alpha_{A}n_{B}^{1}\left((n_{d}^{1}-\bm{\delta}_{B}^{1}+\bm{\delta}_{B}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{B=1\,:\,B\neq d}^{N}n_{B}^{1}-n_{d}^{1}\sum_{B=1\,:B\neq d}^{N}\alpha_{B}
Indeed, by using equation \eqref{boundaryParamRD}, we obtain 

@@

		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)
		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})

@@

		\nu\sigma_{11}\rho_{d}^{\text{left}}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{\text{left}}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})

>>>>

To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{a}^{x})=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$. This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries {\color{blue}is absorbed at extra-site $0$. It fulfils the following equations discrete Laplace equation}

@@

We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ to get

@@

		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})\dt

@@

	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{A=1}^{N}n_{A}^{x}n_{d}^{x+1}-\sum_{B=1}^{N}n_{d}^{x}n_{B}^{x+1}\\

@@

In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{D}^{x+1}$, when $A=d$ (here we call $D=h_{c}(B)$); a contribution $n_{A}^{x}n_{h_{c}(B^{'})}^{x+1}$, where we denoted by $B^{'}\in \{1,\ldots,N\}$ the species of particle such that $h_{c}(B^{'})=d$. Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $h_{c}(B^{'})\neq d$ and $h_{c}(B^{'})\neq N$. Thus we obtain 

@@

		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{A,B=1}^{N}\alpha_{A}n_{B}^{1}\left((n_{d}^{1}-\bm{\delta}_{B}^{1}+\bm{\delta}_{A}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{B=1\,:\,B\neq d}^{N}n_{B}^{1}-n_{d}^{1}\sum_{A=1\,:A\neq d}^{N}\alpha_{A}
Using equation \eqref{boundaryParamRD}, we obtain 

@@

		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)\nonumber
		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})\nonumber

@@

		\nu\sigma_{11}\rho_{d}^{\text{left}}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{\text{left}}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})\nonumber
